Deliminative verbal reduplication in Mandarin Chinese

### 2024-09-09 replies-reviews.tex

In order to get a clearer picture and to find a semantic explanation for these facts, one should look at what these ‘special’ cases of reduplication have in common and try to draw generalizations: why can some stative and achievement verbs reduplicate under certain circumstances, while other cannot? What do these verbs have in common? Can we single out specific subclasses of these verbs which can reduplicate?

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}\label{verbclass}
First, the notion of ``aspect'' adopted in this article has to be explained in more detail.
We adopt the two-component aspect model proposed by \citet{XiaoMcEnery2004} based on \citet{Smith1991}.
The general term ``aspect'' is considered to encompass the following two components:
situation aspect, i.e. ``aspectual information conveyed by the inherent semantic representation of a verb or an idealized situation'' \citep[21]{XiaoMcEnery2004};
and viewpoint aspect, i.e. ``the aspectual information reflected by the temporal perspective the speaker takes in presenting a situation'' \citep[21]{XiaoMcEnery2004}.
Situation aspect can be further modeled as verb classes (dubbed ``Aktionsart'' in the previous version of this paper) at the lexical level
and situation types (the interaction of verb classes and other constituents) at the sentential level \citep[33]{XiaoMcEnery2004}.
The verb classes are determined with verbs in a neutral context (preferably in a perfective viewpoint aspect, with a simple object only when it is obligatory),
where everything that might change the aspectual value of a verb is excluded
and only the inherent features of the verb itself are considered
(see \citealt[52]{XiaoMcEnery2004} for more details).
This does not rule out the fact that the same verb may express different aspectual properties in other contexts,
but its verb class remains the same,
as the aspectual change can be attributable to other components at the sentential level.
Section 2.3.2 is concerned with the interaction of the reduplication with verb classes,
while the Section 2.3.3 discusses the interaction with viewpoint aspect markers.
The combination with other sentential components such as adjuncts is also discussed in Section 2.3.4.%is briefly touched upon below,
%but a detailed discussion has to be left for future research.

Second, there are more examples.
Regarding volitionality, although (15e) in the previous version of the paper is a causative sentence, (13a--b) in the previous version of the paper (17a--b in the current version) are not imperative, conditional or causative (more on this below).
Example (\ref{ex:sheng}) shows the same verb \obj{sheng1} `give birth to' as in (15e) reduplicated in a declarative sentence.
\ea\label{ex:sheng}%我们女人是这么神经质又没用，只能生生孩子，做做女人的活动.。(BCC)
\gll \objex{wo2men} \objex{nv3ren2} \ldots\, \objex{zhi3} \objex{neng2} \obj{sheng1-sheng1} \objex{hai2zi} \ldots \\
we women {} only can give.birth.to-give.birth.to child\\\jambox{(BCC)}
\glt `We women can only give birth to children \ldots'
\z

@@

As for stative verbs, \citet[Sec. 3.3]{Tham2013} uses \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as examples of stative verbs
to contrast adjectives
and what she calls basic change of state verbs such as \obj{bing4} `sick'.
\citet[680]{PeckEtAl2013} also list \obj{xi3huan1} `like' and \obj{xiang1xin4} `believe' as stative verbs.
For these two verbs, examples such as (\ref{ex:xihuan}) and (\ref{ex:xiangxin}) can be found.
\ea\label{ex:xihuan}%这车好型啊！！！。怎么了，我就喜欢喜欢 不行么~ (BCC)
\gll \objex{zhe4} \objex{che1} \objex{hao3} \objex{xing2} \objex{a}! \objex{zen3me} \objex{le}, \objex{wo3} \objex{jiu4} \obj{xi3huan1-xi3huan1} \objex{bu4xing2} \objex{me}?\\
this car so cool \textsc{ptc} what \textsc{ptc} I just like-like cannot \textsc{ptc}\\\jambox{(BCC)}
\glt `This car is so cool! What? I can't just like it for a little bit?'

\ex\label{ex:xiangxin}%谁让我来相信相信 (CCL)
\gll \objex{shei2} \objex{rang4} \objex{wo3} \objex{lai2} \objex{xiang1xin4-xiang1xin4}\\
who let I come believe-believe\\\jambox{(CCL)}
\glt `Who lets me believe him/her?'
\z
However, as the reviewer %\citealt[283]{Ding2010}, \citealt[fn. 3]{BascianoMelloni2017}
and indeed \citet[669--670]{Tham2013} herself noted,
verbs expressing psychological states such as these can have a change of state (COS) interpretation (but not necessarily),
let us look at other examples of stative verbs listed by \citet[680]{PeckEtAl2013} which do not express psychological states,
and examples in  \citet[Sec. 3.3.3]{XiaoMcEnery2004} of individual-level states (ILSs) which only have stative interpretation,
as opposed to stage-level states (SLSs) which can have both stative and dynamic interpretations.\footnote{
Note that most examples of ILSs in \citet[Sec. 3.3.3]{XiaoMcEnery2004} are adjectives.
Since in Mandarin Chinese, adjectives have a different reduplication pattern (see e.g. \citealt[Sec. 2.2]{Tsao2001}, \citealt[Sec. 4.1]{FanSongBond2015}, \citealt[Sec. 3]{Sui2018}),
and further, COS verbs can be systematically derived from adjectives \citep[Sec. 3]{Tham2013},
these predicates are not included in our examples.}
The following examples contain the reduplication of \obj{xiang4} `look like' and \obj{zai4-chang3} `be present on the scene'.
\ea\label{ex:xiang}%范丞丞雪中撑伞这是蒋丞吧王圣迪也拿着滑板！太像顾淼了王安宇你快点也像一像吧！(https://www.163.com/dy/article/FS1FKUC30534DZO1.html (2020/11/22, accessed 2024/03/26))
Context: \objex{Wang2} \objex{Sheng4di2} is the actor of the character \objex{Gu4} \objex{Miao3} in a TV series.
\objex{Wang2} \objex{Ānyu3} is another actor in the series.\\
\\
\gll \objex{Wang2} \objex{Sheng4di2} \ldots\, \objex{tai4} \objex{xiang4} \objex{Gu4} \objex{Miao3} \objex{le}. \objex{Wang2} \objex{Ānyu3} \objex{ni3} \objex{kuai4dian3} \objex{ye3} \obj{xiang4-yi-xiang4} \objex{ba}!\footnotemark\\
Wang Shengdi {} very look.like Gu Miao \textsc{ptc} Wang Anyu you fast also look.like-one-look.like \textsc{ptc}\\
\glt `Wang Shengdi \ldots\,  really looks like Gu Miao. Wang Anyu, you too should just look like (your character) already!'

@@

\ex\label{ex:zaichang}%她此刻正沉浸在一个前所未有的悲剧中，很需要母亲在一在场便能给予她的那点安慰 (CCL)
\objex{ta1} \ldots\, \objex{hen4} \objex{xu1yao4} \objex{mu3qin1} \obj{zai4-yi-zai4-chang3} \ldots\\
she {} very need mother be.present-one-be.present-scene\\\jambox{(CCL)}
\glt `She \ldots\, really needs her mother to be present on scene for a little while \ldots'
\z
\footnotetext{\url{https://www.163.com/dy/article/FS1FKUC30534DZO1.html} (Accessed 26th  March 2024).}

With regard to achievements, the reduplication does not seem to cancel the \textit{telos}.
Applying the classic ``for/in X-time'' test, reduplication is compatible with ``in X-time'' (\ref{ex:telob}) but not with ``for X-time'' (\ref{ex:teloc}).
\ea
\ea[]{\label{ex:teloa}% 一块... 到附近市场买买东西 (CCL)
\gll \objex{yi2kuai4} \ldots\, \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\\
together {} arrive nearby market buy-buy thing\\\jambox{(CCL)}
\glt `(We) together \ldots\, went to the market nearby to buy some things.'}

@@

\ex[]{\label{ex:telob}% 两天后到附近市场买买东西
\gll \objex{liang3} \objex{tian1} \objex{hou4} \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}\\
two day later arrive nearby market buy-buy thing\\
\glt `Two days later, (we) went to the market nearby to buy some things.}

\ex[*]{\label{ex:teloc}%到附近市场买买东西两天
    \gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi} \objex{liang3} \objex{tian1}\\
    arrive nearby market buy-buy thing two day\\
    \glt Intended: `(We) went to the market nearby to buy some things for two days.'}
\z\z
The following continuation that cancels the \textit{telos} is also infelicitous (\ref{ex:telod}).
\ea\label{ex:telod} %到附近市场买买东西 \# 但什么也没买到
\gll \objex{dao4} \objex{fu4jin4} \objex{shi4chang3} \obj{mai3-mai3} \objex{dong1xi}, \# \objex{dan4} \objex{shen2me} \objex{ye3} \objex{mei2} \objex{mai3-dao4}\\
arrive nearby market buy-buy thing {} but anything also not buy-arrive\\
\glt Intended: `(We) went to the market nearby to buy some things, but we didn't buy anything.'
\z

@@

All the examples above show that reduplication is applicable to all verb classes, contrary to common beliefs in the literature,
and thus, a theoretical account of reduplication should not restrict its use to only a subset of verbs.
With our account, we aim to explain as much language data as possible, regardless whether the reviewer considers some examples to be ``special'' or not.

Finally, as we discuss in Section 2.3.1, the semantics of the reduplication has the properties of tansitoriness, holisticity and dynamicity.
This means that the use of reduplication affects the situation aspect at the sentential level.
One might argue that examples such as (\ref{ex:xiang}) and (\ref{ex:zaichang}) above convey dynamic meaning, even though stative verbs are used.
%i.e. they may be interpreted as `become similar to' and `become present' respectively.
However, we argue that the dynamic interpretation does not come from the verb but from reduplication.
These verbs are stative in a neutral context and thus, we consider the intrinsic feature of these verbs to be stative.
The dynamic interpretation only arises when they are used in specific contexts, in this case, when they are reduplicated.
The point of our examples is to show that reduplication can be applied to verbs of all verb classes.

As noted briefly in Section 2.2 in the previous version of the paper,
the reduplication is incompatible with an expression that quantifies the duration or the extent of the event (\ref{ex:syn-quan}),
 because the reduplication already contains a (abstract) quantity meaning, namely a short duration or a small extent (transitoriness),
 which cannot be measured on a concrete scale (\citealt[155]{XiaoMcEnery2004}, \citealt[333]{SuiHu2016}).
 \ea %With an expression of quantity: 
 \label{ex:syn-quan}
 \ea[]{\label{ex:syn-quana}\gll \objex{ta1} \objex{yi4} \objex{tian1} \objex{pao3} \objex{shi2} \objex{li3}.\\
     he one day run ten mile\\ \jambox{\citep[83]{Li1998}}
     \glt `He runs ten miles a day.'}
 \ex[*]{\gll \objex{ta1} \objex{yi4} \objex{tian1} \obj{pao3}-\obj{pao3} \objex{shi2} \objex{li3}.\\
     he one day run-run ten mile\\}
 \z
 \z
% The same can be argued for the incompatibility of reduplication and a quantized object () , as both serve to delimit the event expressed by the base verb \citep[322]{SuiHu2016}.
 %() *我看看三本书。
 This results from the properties of reduplication and does not change the verb class of the predicate.

Due to its unique features compared to the perfective aspect marker \obj{le} and the experiential aspect marker \obj{guo4},
the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
\obj{Le} expresses a situation being realized,
while \obj{guo4} conveys a situation already experienced,
and thus, both rarely occur in future situations.
The use of reduplication does not have these constraints.
This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts,
which are frequently used to describe future situations.

We now  dedicate Section 2.3.4 specifically to discuss the interaction of reduplication with duration\slash frequency phrases and with conditional, imperative and causative sentences 
to highlight the influence of the reduplication on the situation aspect at the sentential level.

@@

1) Compositionality: this test is not reliable. There are phrases whose meaning is not

compositional (see e.g. \textit{kick the bucket}, \textit{shoot the breeze}). Also, take verb-object constructions,
which are ambiguous between words and phrases: e.g. 担心 \obj{dan1-xin1} `take on-heart, worry' has a
non-compositional meaning, suggesting that it is a word, but is separable, suggesting that it is a
phrase (see \citealt{Huang1984}). 
On p. 14, the author(s) state(s): “The meaning of the reduplication is not
compositional, as it does not mean that the event denoted by the verb happens twice or multiple
times, but rather that the event happens for a short duration and/or for low frequency. This non-
compositionality suggests that a reduplication is more word-like.”

If it were compositional, perhaps the meaning should be something like ‘look look” (do the action twice?) but not multiple times. However, I think it is a matter of iconicity rather than compositionality here. In addition, would this imply that the reduplicated verb is a compound? Its meaning and function, though, seem to be closer to inflection or derivation. If it is a derivational item, i.e. a suffix-like element, it can bear a fix aspectual meaning (delimitative aspect): in this sense, the meaning would be compositional.

2) Lexical integrity: if the reduplicated verb is a word, the position of the perfective aspect
marker le is unexpected. In fact, it is never found in between the two constituents of a compound
word, as the author(s) also show(s) in (27c). \citet[1282]{Her2006}, talking about V-给 \obj{gei3} sequences,
states that ``The simple fact that the V-gei sequence cannot be separated, as in (19c) indicates its
lexical integrity'', i.e. they form a single lexical item (寄给了他 \obj{ji4-gei3-le} \obj{ta1} vs. * 寄了给她 \obj{ji4-le} \obj{gei3} \obj{ta1}).
%\itdopt{St. Mü.: fix brackets and references to examples. The quoted text contains Chinese
%  characters. Please try to insert them. Also for the examples below.}
Even if you assume that aspect markers are suffixes (morphological elements), they should not be placed in between the constituents of compounds, because this violates lexical integrity (as shown in ex. 27b by the author(s)): the suffix \obj{le} must be placed after the whole complex verb, which forms a single lexical unit, and not within it. In fact, in (non-separable) verb-object compounds, which are lexical units, 了 \obj{le} is never placed after the verbal constituent (关心了 \obj{guan1-xin1-le} / *关了心 \obj{guan1-le} \obj{xin1} vs. 骑了马 \obj{qi2-le} \obj{ma3}).
It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker \obj{le} can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern.

@@

\itdopt{Stmü: Fix examples and referecnes to them.}

Second, the expansion test suggests that a phrasal dependent (either a modifier or an argument) cannot be inserted into a word.
This is possible for a verbal classifier phrase (\ref{ex:inVCP}), as the object can occur after or in-between.
\ea\label{ex:inVCP}%开两次门
%开门两次
\ea \gll \objex{kai1} \objex{men2} \objex{san1} \objex{ci4}\\
open door three time\\
\glt `open the door three times'

\ex  \gll \objex{kai1}  \objex{san1} \objex{ci4} \objex{men2}\\
open three time door\\
\glt `open the door three times'
\z\z
For reduplication, this is also not possible (\ref{ex:inVV}), as the object cannot be inserted between the two verbs.
\ea\label{ex:inVV}
\ea[]{\gll \obj{kai1}-(\obj{le})-\obj{kai1} \objex{men2}\\
open-\textsc{pfv}-open door\\
\glt `open the door for a little while'}

\ex[*]{%开(了)门(了)开
\gll \obj{kai1}-(\obj{le})-\obj{men2}-\obj{kai1}\\
open-\textsc{pfv}-door-open\\
}
\z\z

The above two tests seem to indicate a lexical analysis.
% If we analyze reduplication as a phrasal operation, we would expect the structure of
% [VP [VP [V-le V]] O]
% Since both phrases are VP, there should be nothing against the following strucutre:
% [VP [VP [V-le O]] V]
% However, this is not possible.

Regarding the position of \obj{le}, there are counter-examples that show V-\obj{le-gei3} (\ref{ex:Vgei}) as well as \obj{guan1-le-}\obj{xin1} `close-\textsc{pfv}-heart, care for' (\ref{ex:guanxin}) are possible.
\ea\label{ex:Vgei}%还有许多女子，将自己的相片，亲笔签字在上面，寄了给他。(CCL)
\gll \ldots\, \objex{xu3duo1} \objex{nv2zi3}, \objex{jiang1} \objex{zi4ji3de} \objex{xiang4pian1} \ldots\, \objex{ji4-le-gei3} \objex{ta1}.\\
{} many women take own photo {} send-\textsc{pfv}-give he\\\jambox{(CCL)}
\glt `Many women \ldots\, sent him photos of themselves.'
\z

\ea\label{ex:guanxin}%许多同志看戏以后，自动的对病员关了心。大家情绪很高... (CCL)
\gll \objex{xu3duo1} \objex{tong2zhi4} \ldots\, \objex{zi4dong4de} \objex{dui4} \objex{bing4yuan2} \objex{guan1-le-}\obj{xin1}.\\
many comrade {} voluntarily to patient close-\textsc{pfv}-heart\\\jambox{(CCL)}
\glt `Many comrades \ldots\, voluntarily cared for the patients.'
\z

@@

In any case, since reduplication is not compounding (\citealt[149--150]{Sui2018}; \citealt{GaoEtAl2021} provides empirical evidence.),
and the patterns discussed here constitute a different process than the AABB pattern
(see the discussion on \citealt{Xie2020} in our paper, also \citealt[Sec. 4.3]{Deng2013}, \citealt[Sec. 2]{SuiHu2016}, \citealt{Sui2018} and \citealt{Wang2023}),
it is not surprising that \textit{le} occurs at a different position.

The comparison with Parallel Verb Compounds and Serial Verb Constructions only serves to facilitate understanding
by contrasting the behaviors of different multi-verb constructions in Mandarin Chinese,
but this does not contribute to the arguments in any substantial way.
Due to the critics from the reviewers, this comparison is removed.
